---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mcmodel

<!-- badges: start -->
`r badger::badge_github_version("gaospecial/mcmodel", color = "blue")`
<!-- badges: end -->

The goal of `mcmodel` is to standardize the method for melting curve data modelling and prediction.

## Installation

You can install the development version of mcmodel from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gaospecial/mcmodel")
```

```{r}
library(mcmodel)
library(dplyr)
library(readr)
library(ggplot2)
```

```{r include=FALSE}
devtools::load_all()
```


## 读取熔解曲线数据


```{r}
# sample data
file = system.file("quantstudio", "quantstudio-export.txt.gz", package = 'mcmodel')
all_data = read_quantstudio(file)
```


`all_data` contains all information in that file, including experimental setting, melting curve data, and so on.

```{r}
all_data
```

We use `get_quantstudio_melting_curve()` to get melting curve dataset.

```{r}
melting_curve_data = get_quantstudio_melting_curve(all_data)
melting_curve_data
```

In this experiment, these are > 81k observations of six variables.

## 绘制熔解曲线

If you want to plot the melting curve, just use the `plot_quantstudio_melting_curve()`.

```{r}
plot_quantstudio_melting_curve(melting_curve_data)
```

Type `?plot_quantstudio_melting_curve` in your console, and you may find that there is a extra argument for this function.

```{r}
plot_quantstudio_melting_curve(melting_curve_data, y = "derivative")
```

If you want to scale up this plot,

```{r}
plot_quantstudio_melting_curve(melting_curve_data, y = "derivative") +
  coord_cartesian(xlim = c(80, 90))
```

Likewise, you may get the amplification data, and plot it.

```{r}
amplification_data = get_quantstudio_amplication(all_data)
plot_quantstudio_amplification_curve(amplification_data)
```

This is just a small step to proceed this program, and it is the way what I want.

### Plot Community Structure in 384-well Plate

空白的平板，这样画：

```{r}
plot_384() +
  geom_point(color = "grey", size = 5)
```

画单一物种的数量。首先画大肠杆菌的含量（log2）。

Plate.

```{r}
file =  system.file("quantstudio", "quantstudio-plate.csv.gz", package = 'mcmodel')
concentration = read_csv(file)
concentration
```

```{r}
plot_384_single_concentration(concentration, species = "label_E")
```

其次，用另外一个颜色画假单胞菌的含量。

```{r}
plot_384_single_concentration(concentration, species = "label_P")
```

画每个孔的结构。

```{r}
plot_384_community_structure(concentration)
```

## 使用 MeltingCurve 对象

使用 `MeltingCurve` 对象可以确保数据不会被意外修改。

**创建 MC 对象**

从实验原始数据创建 MC 对象。

```{r}
all_data
mc = quantstudio2mc(all_data)
```

画熔解曲线。

```{r}
plot_mc(mc, show_tm = FALSE)
```

过滤熔解曲线的温度范围，以及反应孔。

```{r}
mc_narrow = filterData(mc, 82, 86, c("A1","A2","B1","B2"))
plot_mc(mc_narrow, show_tm = FALSE)
```

对熔解曲线进行重采样。

```{r}
mc_low = transformData(mc_narrow, step = 0.5)
plot_mc(mc_low)
```

将对象转变成建模数据集。

```{r}
df = mc_tbl2wider(mc_low)
df
```

主成分分析。

```{r}
pca = mc_pca(mc_low)
mc_pca_plot(pca)
```
